### 2017-04-06 paper/evaluation.tex
pass on RQ4

Research questions \numRQC{} and \numRQE{} investigate to which extent
parallelization is used in practice.  It is important to investigate
adoption as it is possible that developers may use alternative
mechanisms to execute tests.

\begin{itemize}
    \item \numRQC. \emph{\RQC}
\end{itemize}

To answer \numRQC{}, we selected all projects that ran in at least one
minute, \ie, projects from the \medg{} and \longg{} groups.  This set
includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
looked for dynamic and static manifestations of parallelism.
Section~\ref{sec:rqC-1} and~\ref{sec:rqC-2} report results for each of
these cases.

\vspace{1ex}
\subsubsection{Test execution with parallelism enabled by default}
\label{sec:rqC-1}

To find dynamic evidence of parallelism, we ran the test suites from
our set of \numMedLong{} projects to output all key-value pairs of
Maven parameters.  To that end, we used the option~\CodeIn{-X} to
produce debug output and the option~\CodeIn{-DskipTests} to skip
execution of tests.  We observed that only bootstrapping execution
suffices to discover which parallel configuration modes Maven will
actually use.  According to Maven's
documentation~\cite{maven-surefire-plugin}, any parallelism
configuration depends either on (1) the parameter \CodeIn{parallel} to
define the parallelism mode within a JVM followed by the parameter
\CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
  in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).  Large projects may contain several test suites
distributed on different Maven modules with different
configurations. In this case, we collect the Maven output from each
module discarding duplicates. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.

>>>>

The dimension adoption focuses on the usage of parallelism in
open-source projects.  It evaluates (\numRQC) how often open-source
projects use parallelization schemes and (\numRQE) how developers
involved in costly projects, not using parallelization, perceive this
technology.

\begin{itemize}
    \item \numRQC. \textbf{\RQC{}}
\end{itemize}

To answer \numRQC{}, we selected all projects from the \medg{} and
\longg{} groups, \ie, projects that ran in at least one minute.  This
set includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
looked for dynamic and static manifestations of parallelism.

%% The
%% following section report results for each of these cases.

\vspace{1ex}
\subsubsection{Dynamic checking}
\label{sec:rqC-1}

To find dynamic evidence of parallelism, we ran the test suites from
our set of \numMedLong{} projects to output all key-value pairs of
Maven parameters.  To that end, we used the option~\CodeIn{-X} to
produce debug output and the option~\CodeIn{-DskipTests} to skip
execution of tests.  We observed that only bootstrapping the Maven
process suffices to discover which parallel configuration modes it
will use to run tests.  According to Maven's
documentation~\cite{maven-surefire-plugin}, a parallel configuration
depends either on (1) the parameter \CodeIn{parallel} to define the
parallelism mode within a JVM followed by the parameter
\CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
  in old versions of Maven Surefire} to define the number of forked
JVMs.  As such, we captured, for each project, all related key-value
pairs of Maven parameters and mapped those pairs to one of the
possible parallelization modes.  For instance, if a given project
contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel}.  If the parameter
\CodeIn{parallel} is set to \CodeIn{methods} the detected mode will be
\ForkParMeth{}.  Large projects may contain several test suites
distributed on different Maven modules potentially using different
configurations.  For those cases, we collected the Maven output from
each module discarding duplicates as to avoid inflating results. For
instance, if a project contains two modules using the same
configuration, we counted only one occurrence.

\Mar{---- estou aqui}
